Enhanced Overall Local Accuracy Framework For Addressing Feature Bias and Data Imbalance in ASD Classification

### 2025-06-05 Paper/BichHao/main.tex
lan1 final

Y. Zeng, J. Liu, H. Lam, and H. Namkoong.~\cite{b7} explored using Large Language Model (LLM) embeddings to improve the robustness of tabular classifiers like XGBoost and logistic regression under distributional shifts. By combining LLM-derived features with original tabular features and applying group-wise robust optimization at test time, their method enhances generalization performance across diverse datasets, effectively handling covariate and label shifts.

@@

\bibitem{b6} Z. Liu \textit{et al.}, ``Ola: Pushing the frontiers of omni-modal language model with progressive modality alignment,'' \textit{arXiv preprint}, arXiv:2502.04328, 2025. Available: \url{https://arxiv.org/abs/2502.04328}

\bibitem{b7} Y. Zeng, J. Liu, H. Lam, and H. Namkoong, ``LLM embeddings improve test-time adaptation to tabular Y|X-shifts,'' \textit{arXiv preprint}, arXiv:2410.07395, 2024. Available: \url{https://arxiv.org/abs/2410.07395}

@@

% \bibitem{b16} Overall Local Accuracy. Available: \url{https://deslib.readthedocs.io/en/latest/modules/dcs/ola.html}

>>>>

Y. Zeng, J. Liu, H. Lam, and H. Namkoong.~\cite{b6} explored using Large Language Model (LLM) embeddings to improve the robustness of tabular classifiers like XGBoost and logistic regression under distributional shifts. By combining LLM-derived features with original tabular features and applying group-wise robust optimization at test time, their method enhances generalization performance across diverse datasets, effectively handling covariate and label shifts.

@@

% \bibitem{b6} Z. Liu \textit{et al.}, ``Ola: Pushing the frontiers of omni-modal language model with progressive modality alignment,'' \textit{arXiv preprint}, arXiv:2502.04328, 2025. Available: \url{https://arxiv.org/abs/2502.04328}

\bibitem{b6} Y. Zeng, J. Liu, H. Lam, and H. Namkoong, ``LLM embeddings improve test-time adaptation to tabular Y|X-shifts,'' \textit{arXiv preprint}, arXiv:2410.07395, 2024. Available: \url{https://arxiv.org/abs/2410.07395}

@@

\bibitem{b16} Overall Local Accuracy. Available: \url{https://deslib.readthedocs.io/en/latest/modules/dcs/ola.html}
